The effect of starvation on the dynamics of consumer populations

### 2016-07-09 Manuscript/Yeakel_Kempes_Redner-7-5-2016.tex
manuscript updates

%Bifurcation space as a function of mass
As the allometric derivations of NSM rate laws reveal, $\sigma$ and $\rho$ are not independent parameters, such that the bifurcation space shown in Fig. \ref{Hopfb} cannot be freely navigated if assuming biologically reasonable parameterizations.
Given the parameterization for mammals shown in Table \ref{xx} with mass $M$ as the only free parameter, rates of starvation and recovery are constrained to a fairly small window of potential values.
Importantly, for larger organismal masses, the distance between $\sigma(M)$ and $\rho(M)$ compared to both the TC and Hopf bifurcations is increased.
This suggests that small mammals are more prone to population oscillations -- including both stable limit cycles as well as transient cycles -- than large mammals, a general prediction that appears to qualitatively hold.

>>>>

%Bifurcation space as a function of mass
As the allometric derivations of NSM rate laws reveal, $\sigma$ and $\rho$ are not independent parameters, such that the bifurcation space shown in Fig. \ref{Hopfb} cannot be freely navigated if assuming biologically reasonable parameterizations.
Given the parameterization for mammals shown in Table \ref{xx} with mass $M$ as the only free parameter, rates of starvation and recovery are constrained to a fairly small window of potential values.
Importantly, for larger organismal masses, the distance between $\sigma(M)$ and $\rho(M)$ compared to both the TC and Hopf bifurcations is increased.
Uncertainty in allometric parameters (20\% variation around the mean; Fig. \ref{xx}) results in little difference in the position of both bifurcations as well as consumer energetic rates.
This suggests 
1)that small mammals are more prone to population oscillations -- including both stable limit cycles as well as transient cycles -- than large mammals, and
2) the decreasing distance to the Hopf bifurcation with lower body sizes is suggestive of a dynamic barrier to the mass of endothermic organisms.
Although the prediction of oscillations with smaller body sizes  generally holds, empirical observations of large animal population cycles are plagued by long generation times and the influence of top-down effects [REFS].
